---
title: "Quality Control"
output: html_document
params:
  jsonfile : 'example/PFAC30PAR_PFCA2_mzML_cmpd2628.JSON'
---

```{r echo=FALSE, include=FALSE}
result_json <- jsonlite::read_json(params$jsonfile)
```

# Peak Name: **`r result_json$peak[[1]]$name`** 
# File Name: **`r result_json$sample$name`**



### MS1 Chromatogram

```{r echo=FALSE}
  chrom = do.call(rbind, lapply(result_json$msdata, function(x) if (x$ms_n == 1) {data.frame(time = x$scantime, intensity = x$base_int)}))
  plot(x = chrom$time, y = chrom$intensity, type = "l")
```

## Quality Control Check

### *Measured Accuracy of Precursor Ion*

```{r echo = FALSE}
  knitr::kable(do.call(rbind, lapply(result_json$qc[[1]], function(x) x)))
```

### *MS1 Isotopic Pattern Match*

```{r echo = FALSE}
  knitr::kable(do.call(rbind, lapply(result_json$qc[[2]], function(x) x)))
```

### *Precursor Ion in MS1 Spectrum*

```{r echo = FALSE}
  knitr::kable(do.call(rbind, lapply(result_json$qc[[3]], function(x) x)))
```

### *Annotated Fragment Ions Detected*

```{r echo = FALSE}
if (length(result_json$qc) >= 4) {
  knitr::kable(do.call(rbind, lapply(result_json$qc[[4]], function(x) x)))
}
```

### *Measured Accuracy of Annotated Fragments*

```{r echo = FALSE}
if (length(result_json$qc) >= 5) {
  knitr::kable(do.call(rbind, lapply(result_json$qc[[5]], function(x) x)))
}
```

### *Fragments are Subset of Parent Formula*

```{r echo = FALSE}
if (length(result_json$qc) >= 6) {
  knitr::kable(do.call(rbind, lapply(result_json$qc[[6]], function(x) x)))
}
```

### *SMILES Calculated Formula Matches Reported Formula*

```{r echo = FALSE}
  if (length(result_json$qc) >= 7) {
    knitr::kable(do.call(rbind, lapply(result_json$qc[[7]], function(x) x)))
  }
```